DATA 621 - Business Analytics and Data Mining

### 2020-11-08 HW4/HW4_Draft.Rmd
Use R2 not adj R2, clean up text

# Get the names of the variables and which ones are numeric
nmtrn <- names(DT)
nmtrnNUM <- names(DT[, .SD, .SDcols = sapply(DT, is.numeric)])
nmtrnDUB <- names(DT[, .SD, .SDcols = sapply(DT, is.double)])
nmtrnFAC <- setdiff(nmtrn, nmtrnNUM)
# Drop INDEX and target variables from name list
nmtrnNUM <- nmtrnNUM[-(1:3)]
```

@@

# SELECT MODELS
## Model Selection Criteria
For that *classification* algorithm, we will look at accuracy, AUC, and F1, and
select the model which performs best two out of three in those metrics. For the
*regression* algorithm, we will look at RMSE and MAE (since the values must
be positive) and select the model which performs best on both, Ties will be
broken by adjusted \(R^2\).

```{r setUpCompTables}
# Create comparison tables
freqCompTable <- data.frame(Models = c('Model 1', 'Model 2', 'Model 3'),
                            ACC = double(3),
                            F1 = double(3),
                            AUC = double(3))
sevCompTable <- data.frame(Models = c('Model 1', 'Model 2', 'Model 3'),
                           RMSE = double(3),
                           MAE = double(3),
                           adjR2 = double(3))
```

@@

```{r validateM1S}
# Model 1 Severity: process validation data similar to training data
tstSev <- tstX[TARGET_AMT > 0, TARGET_AMT]
nobstst <- length(tstSev)
np <- summary(m1SevFit$finalModel)$df[3]
tstDumSev <- dummyVars(TARGET_AMT ~ . - INDEX - TARGET_FLAG,
                       data = tstX[TARGET_AMT > 0])
tstXSD <- predict(tstDumSev, newdata = tstX[TARGET_AMT > 0])
tstXSDpp <- preProcess(tstXSD, method = c('nzv', 'knnImpute'),
                       k = 3, knnSummary = median)
tstXSDI <- predict(tstXSDpp, newdata = tstXSD)

# Model 1 Severity: predict on validation data
m1Spred <- predict(m1SevFit, newdata = tstXSDI)
# Model 1 Severity: Calculate accuracy statistics
m1Ssum <- postResample(m1Spred, tstSev)
sevCompTable[1, 2] <- m1SRMSE <- m1Ssum[1]
sevCompTable[1, 3] <- m1SMAE <- m1Ssum[3]
m1SAR2 <- 1 - (1 - m1Ssum[2]) * (nobstst - 1) / (nobstst - np - 1)
sevCompTable[1, 4] <- m1SAR2
```

Severity Model 1  returns an RMSE of `r round(m1SRMSE, 1)`, an MAE of
`r round(m1SMAE, 1)`, and an adjusted \(R^2\) of `r round(m1SAR2, 4)`.

@@

# Accuracy Statistics
m2Ssum <- postResample(m2Spred, tstSev)
sevCompTable[2, 2] <- m2SRMSE <- RMSE(m2Spred, m2.test.r)
sevCompTable[2, 3] <- m2SMAE <- MAE(m2Spred, m2.test.r)
sevCompTable[2, 4] <- m2SAR2 <- R2(m2Spred, m2.test.r)
```

Severity Model 2 returns an RMSE of `r round(m2SRMSE, 1)`, an MAE of
`r round(m2SMAE, 1)`, and an adjusted \(R^2\) of `r round(m2SAR2, 4)`.

>>>>

# Get the names of the variables and which ones are numeric
nmtrn <- names(DT)
nmtrnNUM <- names(DT[, .SD, .SDcols = sapply(DT, is.numeric)])
nmtrnFAC <- setdiff(nmtrn, nmtrnNUM)
# Drop INDEX and target variables from name list
nmtrnNUM <- nmtrnNUM[-(1:3)]
```

@@

# SELECT MODELS
## Model Selection Criteria
For that *classification* algorithm, we will look at accuracy, AUC, and F1, and
select the model which performs best two out of three in those metrics. For the
*regression* algorithm, we will look at RMSE and MAE (since the values must
be positive) and select the model which performs best on both, Ties will be
broken by \(R^2\).

```{r setUpCompTables}
# Create comparison tables
freqCompTable <- data.frame(Models = c('Model 1', 'Model 2', 'Model 3'),
                            ACC = double(3),
                            F1 = double(3),
                            AUC = double(3))
sevCompTable <- data.frame(Models = c('Model 1', 'Model 2', 'Model 3'),
                           RMSE = double(3),
                           MAE = double(3),
                           R2 = double(3))
```

@@

```{r validateM1S}
# Model 1 Severity: process validation data similar to training data
tstSev <- tstX[TARGET_AMT > 0, TARGET_AMT]
tstDumSev <- dummyVars(TARGET_AMT ~ . - INDEX - TARGET_FLAG,
                       data = tstX[TARGET_AMT > 0])
tstXSD <- predict(tstDumSev, newdata = tstX[TARGET_AMT > 0])
tstXSDpp <- preProcess(tstXSD, method = c('nzv', 'knnImpute'),
                       k = 3, knnSummary = median)
tstXSDI <- predict(tstXSDpp, newdata = tstXSD)

# Model 1 Severity: predict on validation data
m1Spred <- predict(m1SevFit, newdata = tstXSDI)
# Model 1 Severity: Calculate accuracy statistics
m1Ssum <- postResample(m1Spred, tstSev)
sevCompTable[1, 2] <- m1SRMSE <- m1Ssum[1]
sevCompTable[1, 3] <- m1SMAE <- m1Ssum[3]
sevCompTable[1, 4] <- m1SR2 <- m1Ssum[2]
```

Severity Model 1  returns an RMSE of `r round(m1SRMSE, 1)`, an MAE of
`r round(m1SMAE, 1)`, and an \(R^2\) of `r round(m1SR2, 4)`.

@@

# Accuracy Statistics
m2Ssum <- postResample(m2Spred, tstSev)
sevCompTable[2, 2] <- m2SRMSE <- RMSE(m2Spred, m2.test.r)
sevCompTable[2, 3] <- m2SMAE <- MAE(m2Spred, m2.test.r)
sevCompTable[2, 4] <- m2SR2 <- R2(m2Spred, m2.test.r)
```

Severity Model 2 returns an RMSE of `r round(m2SRMSE, 1)`, an MAE of
`r round(m2SMAE, 1)`, and an \(R^2\) of `r round(m2SR2, 4)`.
